Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-19 paper/ijcai/paper.tex
fixes in abstract

\begin{abstract}
Several approaches have been proposed in the literature to improve
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
very popular fault diagnosis techniques and normally seen as
complementary.  This paper reports the outcome of a comprehensive
study with the goal of demystifying the impact of combining \ds{} with
\sfl{}.  We suspect that several highly suspicious components---often
involved in failing, but seldom in passing executions---may be
unrelated to the bug. With the aforementioned combination, such
components could be identified and their suspiciousness reduced.  This
study also discusses the impact of the dynamic slicing key
limitation---the risk of missing faulty statements. Our results show
that, in practice, \ds{} rarely misses faulty statements (\Fix{X}
misses in \Fix{Y} cases) and that the \ds{}-\sfl{} combination
improves the diagnostic accuracy in \Rui{x\% on average}. \Mar{check
  if you agree on this...} To sum, we found that, despite tacit
opinions of the reserach commuinity about the usefulness of \ds{} in
automated debugging, we found the combination practical and effective,
and encourage new \sfl{} techniques to be evaluated against that
optimization.
%, a technique we coin as Tandem-FL
%% hence leading to the root cause of
%% observed failures faster.
\end{abstract}

>>>>

\begin{abstract}
Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis.  Dynamic Slicing (\ds{}) and
Spectrum-based Fault Localization (\sfl{}) are very popular fault diagnosis
techniques and normally seen as complementary.  This paper reports the outcome
of a study using real-world applications with the goal of demystifying the
impact of combining \ds{} with \sfl{}.  We suspect that several highly
suspicious components---often involved in failing, but seldom in passing
executions---may be unrelated to the bug. With the aforementioned combination,
such components could be identified and their suspiciousness reduced.  This
study also discusses the impact of the dynamic slicing key limitation---the risk
of missing faulty statements. Our results show that, in practice, \ds{} rarely
misses faulty statements (\Fix{X} misses in \Fix{Y} cases) and that the
\ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic accuracy
in \Rui{x\% on average}. To sum, we found that, despite tacit opinions of the
research community about the usefulness of \ds{} in automated debugging, we
found the combination practical and effective, and encourage new \sfl{}
techniques to be evaluated against that optimization.
\end{abstract}
